Housing Default Handovers

### 2024-02-29 minos/validation/housing_handovers.Rmd
getting manchester scaled pop and diff map working

>>>>

net.income.spag <- rbind(raw.inc, base.inc)

density_ridges(net.income.spag, 'net_hh_income',
               save=TRUE, 
               save.path=save.path)

pidp_sample <- sample(unique(net.income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
net.income.spag.sample <- net.income.spag[which(net.income.spag$pidp %in% pidp_sample), ]
spaghetti_plot(net.income.spag.sample, 'net_hh_income',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(net.income.spag.sample, 'net_hh_income',
               save = shall.we.save,
               save.path = save.path)
